---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The French official open data portal offers a huge quantity of information. They also provide a well structured [API](https://doc.data.gouv.fr/api/reference/). The [BARIS](https://github.com/feddelegrand7/BARIS) package allows you to exploit this API in order to get the required data from the portal. 

> Within the portal there is the concept of a data set which contains one or several data frames or resources. So, if I use the resource term, you need to apprehend it as the data frame inside a data set. 


The package is available on CRAN, you can also install the development version from Github: 


```{r, eval=FALSE}

install.packages("BARIS")

```


Too much talking, let's dive into a reproducible example.


# BARIS_search()

The `BARIS_search()` function allows you to search for a specified data set. **A quick tip: within your query, use plain Nouns and avoid prepositions and determinants: le, la, de, des, en, à ... and so on** :

```{r message=FALSE, warning=FALSE}
library(BARIS)

BARIS_search(query = "Monuments Historiques Marseille")

```

Cool we have our data set ... but wait it would be better to get some explanation about it. 

# BARIS_explain()

The `BARIS_explain()` function provides a description of a data set. The function takes one argument which is the ID of the data set: 


```{r}

BARIS_explain(datasetId = "5cebfa8306e3e77ffdb31ef5")


```


Don't panic if you're not a french speaker. You can always use the great [googleLanguageR](https://CRAN.R-project.org/package=googleLanguageR). 


Now, it's time to list the resources contained within this data set !!!



# BARIS_resources()


The `BARIS_resources` function displays the available resources or data frames within a data set. The function takes as argument the ID of the data set: 

```{r}
BARIS_resources(datasetId = "5cebfa8306e3e77ffdb31ef5")

```


You can see from above that the data set has two resources, a *csv* and a *pdf*. Now, we've reached the interesting part: extracting the data frame that you'll work on ! 

# BARIS_extract()

Using `BARIS_extract()` you can extract directly into your R session the needed data set. Currently, “only” theses formats are supported: json, csv, xls, xlsx, xml, geojson and shp, nevertheless you can always rely on the url of the resource to download it manually.

In order to use the function you'll have to specify two arguments: The ID of the resource and its format.

> You can visually catch the structure difference between the ID of a data set and the ID of a resource. 


```{r}

data <- BARIS_extract(resourceId = "59ea7bba-f38a-4d75-b85f-2d1955050e53", format = "csv")

head(data)

```


End of the vignette. 
